% Copyright 2019, 2021 Anthony Di Pietro
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
%
% This work has the LPPL maintenance status `maintained'.
%
% The Current Maintainer of this work is Anthony Di Pietro.
%
% This work consists of the files uwa-pif.dtx, uwa-pif.ins, and
% uwa-pif-example.tex and the derived files uwa-pif.cls and uwa-pif.pdf.

\documentclass{uwa-pif}

\author{John Smith}
\school{School of Psychological Science}
\mbdp{000}
\phone{+61 8 6488 0000}
\email{john.smith@uwa.edu.au}
\project{My Research Project}
\researchers{Joe Bloggs (PhD Student) \\ John Smith (Supervisor)}

\begin{document}

\section{Invitation:}

You are invited to participate in a research project. You are asked
to take part in this project because you are registered as a research
participant in our database.

\section{Aim of the Study (What is the project about?)}

This project examines how people think and behave.

\section{What does participation involve?}

You will be asked to complete a task. You may also be asked to complete
surveys that provide demographic information about yourself. This information
will be anonymised, and so will not be linked to your identity.

We estimate that participating in this study will take 15~minutes.

\section{Voluntary Participation and Withdrawal from the Study}

Participation in this study is entirely voluntary, and does not
prejudice any right to compensation, which you may be entitled to
under statute or common law. Should you wish to withdraw from the study
before completing it, your responses will be discarded. Your data will
be stored in a deidentified fashion, meaning that no identifying information
will be associated with the data we collect from you in the experiment.
Accordingly, you will not be able to withdraw your consent for us to
use your data once the study has been completed.

\section{Your privacy}

On publication of this work, your responses (without any personally
identifying information) will be made publicly available by banking
the data from the entire study on data sharing websites.

\section{Possible Benefits}

The data from this project may allow researchers (including us) to better
understand how people think and behave.

\section{Possible Risks and Risk Management Plan}

There are no foreseeable risks associated with this study.

\section{Reimbursement}

You will receive a payment of £2 as reimbursement for your participation.

\section{Contacts}

If you would like to participate or discuss any aspect of this study,
please feel free to contact Mr Joe Bloggs (PhD Student,
\href{mailto:joe.bloggs@research.uwa.edu.au}{joe.bloggs@research.uwa.edu.au},
\href{tel:+61-000-000-000}{+61 000 000 000}) or Dr John Smith (Supervisor,
\href{mailto:john.smith@uwa.edu.au}{john.smith@uwa.edu.au},
\href{tel:+61-8-6488-000}{+61 8 6488 000}).

\section{About This Document}

You are entitled to retain a copy of this document. If you would prefer
a PDF copy, email the above contacts to obtain one.

\end{document}
